Parsing Postfix log files

### 2009-02-25 doc/logparser-acronyms.tex
Proofread bibliography and made corrections.

\newglossaryentry{DNSBL}{
    type=\acronymtype,
    name={DNSBL},
    description={DNS Blacklist},
    first={DNS Blacklist (DNSBL)}
}
\newglossaryentry{DNSBL glossary}{
    name={DNS Blacklist},
    description={
        A DNS Blacklist~\cite{Wikipedia-DNSBL} is a simple collaborative
        anti-spam technique used to reject or penalise mail sent from mail
        servers believed to be the source of large volumes of spam.  The
        criteria used when deciding whether or not to include an IP address
        on a DNSBL vary widely between DNSBLs, so before using one it is
        very important to check their listing policies.  To use a DNSBL the
        mail server makes a DNS request incorporating the IP address of the
        client; if the requested hostname exists the client is on the
        DNSBL, and the mail server can decide what course of action to
        take.
    }
}

@@

\newglossaryentry{NLP}{
    type=\acronymtype,
    name={NLP},
    description={Natural Language Processing},
    first={Natural Language Processing (NLP)}
}
\newglossaryentry{NLP glossary}{
    name={Natural Language Processing},
    description={
        Natural Language Processing~\cite{Wikipedia-nlp} is an area of
        research that attempts to increase our understanding of the
        languages normally used by humans (e.g.\ English, Spanish,
        Japanese), with the goal of writing programs that can understand
        human languages.
    }
}

>>>>

\newglossaryentry{DNSBL}{
    type=\acronymtype,
    name={DNSBL},
    description={DNS Blacklist},
    first={DNS Blacklist (DNSBL)}
}
\newglossaryentry{DNSBL glossary}{
    name={DNS Blacklist},
    description={
        A DNS Blacklist is a simple collaborative anti-spam technique used
        to reject or penalise mail sent from mail servers believed to be
        the source of large volumes of spam.  The criteria used when
        deciding whether or not to include an IP address on a DNSBL vary
        widely between DNSBLs, so before using one it is very important to
        check their listing policies.  To use a DNSBL the mail server makes
        a DNS request incorporating the IP address of the client; if the
        requested hostname exists the client is on the DNSBL, and the mail
        server can decide what course of action to take.
    }
}

@@

\newglossaryentry{NLP}{
    type=\acronymtype,
    name={NLP},
    description={Natural Language Processing},
    first={Natural Language Processing (NLP)}
}
\newglossaryentry{NLP glossary}{
    name={Natural Language Processing},
    description={
        Natural Language Processing is an area of research that attempts to
        increase our understanding of the languages normally used by humans
        (e.g.\ English, Spanish, Japanese), with the goal of writing
        programs that can understand human languages.
    }
}

### 2009-02-25 doc/logparser-glossary.tex
Proofread bibliography and made corrections.

\newglossaryentry{Joe job}{name={Joe Job},description={
    A joe~job describes spam mail sent using a faked sender address with
    the intention of sullying the good name of the user of that address.
    Joe~jobs are one cause of backscatter\glsadd{Backscatter}.
}}

>>>>

\newglossaryentry{Joe-job}{name={Joe~Job},description={
    A joe~job describes spam mail sent using a faked sender address with
    the intention of sullying the good name of the user of that address.
    Joe~jobs are one cause of backscatter\glsadd{Backscatter}.
}}

### 2009-02-25 doc/logparser-implementation.tex
Proofread bibliography and made corrections.

    \item [\daemon{smtpd}, \daemon{postsuper}:] Mail accepted from a remote
        client, then deleted by the administrator before any delivery
        attempt was made (the unwanted mail is typically due to a mail loop
        or joe~job).  Notice that \daemon{postsuper} is required, not
        optional, for this combination.

@@

Postfix logs the recipient address when delivery of a mail is attempted, so
if delivery has yet to be attempted the parser cannot determine the
recipient address or addresses.  This is a problem when mail is arriving
faster than Postfix can attempt delivery, and the administrator deletes
some of the mail (because it is the result of a mail loop\glsadd{mail
loop}, mail bomb\glsadd{mail bomb}, or joe~job\glsadd{Joe job}) before
Postfix has had a chance to try to deliver it.  In this case the recipient
address will not have been logged, so a dummy recipient address needs to be
added, as every mail is required by the database schema
(\sectionref{results table}) to have at least one recipient.  This
complication has been observed in XXX/\numberOFlogFILES{} log files, but
typically when it does occur there will be many instances of it, closely
grouped.

>>>>

    \item [\daemon{smtpd}, \daemon{postsuper}:] Mail accepted from a remote
        client, then deleted by the administrator before any delivery
        attempt was made (the unwanted mail is typically due to a mail loop
        or joe~job\glsadd{Joe-job}).  Notice that \daemon{postsuper} is
        required, not optional, for this combination.

@@

Postfix logs the recipient address when delivery of a mail is attempted, so
if delivery has yet to be attempted the parser cannot determine the
recipient address or addresses.  This is a problem when mail is arriving
faster than Postfix can attempt delivery, and the administrator deletes
some of the mail (because it is the result of a mail loop\glsadd{mail
loop}, mail bomb\glsadd{mail bomb}, or joe~job\glsadd{Joe-job}) before
Postfix has had a chance to try to deliver it.  In this case the recipient
address will not have been logged, so a dummy recipient address needs to be
added, as every mail is required by the database schema
(\sectionref{results table}) to have at least one recipient.  This
complication has been observed in XXX/\numberOFlogFILES{} log files, but
typically when it does occur there will be many instances of it, closely
grouped.
